Sketch Recognition and Understanding

### 2009-09-26 draft/Results.tex

%We performed several experiments to evaluate the presented recognition system. Firstly we tested recognition accuracy of shapes in the data set with both algorithms (\textsl{AlgS1} and \textsl{AlgS2}). We also implemented the segmentation algorithm described in \cite{earlyprocess} (\textsl{Alg3} in section \ref{sec:BenchMarckAlgorithm} )  to use as reference to compare it with our swarm algorithms. Figure \ref{fig:test1},\ref{fig:testEL} and \ref{fig:testLD}  shows the accuracy achieved by each algorithm. The two swarm algorithms were tested with and without the ellipse fitting module. The ellipse fitting module appears to be superior. The result shows that combining both algorithms (\textsl{AlgS1} and \textsl{AlgS2}) outperform any single algorithm. %show that combining algorithms achieve higher accuracy than any single algoirthm. 
%improves the results.% with both the \textit{DPSO} algorithms.% The results show that both \textit{DPSO} algorithms achieve better result than other algorithms. 
\begin{figure}
	\centering		
	 \includegraphics[scale=0.4]{paperImages/testAlg.jpg.eps}
	 	\caption{Algorithm comparison on HS-DB} The recognition rate of different algorithms. 
	 	\label{fig:test1}
	%\caption{Experiments results :} a)    b) c) 
\end{figure} 
\begin{figure}
	\centering		
	 \includegraphics[scale=0.8]{results/AlgLD.eps}
	 	\caption{Algorithm comparison on LD-DB} The recognition rate of different algorithms. 
	 	\label{fig:testLD}
	%\caption{Experiments results :} a)    b) c) 
\end{figure}

\begin{figure}
	\centering		
	 \includegraphics[scale=0.8]{results/AlgEL.eps}
	 	\caption{Algorithm comparison on EL-DB} The recognition rate of different algorithms. 
	 	\label{fig:testEL}
	%\caption{Experiments results :} a)    b) c) 
\end{figure}

@@

 The effects of symbol complexity in a dataset were testing in the following experiment. These experiments test how many samples will be required to finally obtain good performance from the recognizer system. In the following experiments, we tested the system using different number of sample per category. 
 Figure \ref{fig:Alg1Ds} and \ref{fig:Alg2Ds} shows that Hs-DB requires more number of sample for training to achieve same result as in other data sets. This is due that it contains less signal and conceptual variation that the other two datasets. Figure \ref{fig:samplesofHS-DB.jpg} shows sample of data collected from one user in Hs-Db it is clear that it has reasonable amount of variation between users but it is limited. Recognizing symbols that contains high variation in drawing style using fewer symbols in training prove the efficiency of our system.
 \begin{figure}
	\centering
		\includegraphics{results/Alg1Ds.eps}
	\caption{AlgS1 on different datasets}
	\label{fig:Alg1Ds}
\end{figure}
\begin{figure}
	\centering
		\includegraphics{results/Alg2Ds.eps}
	\caption{AlgS2 on different Datasets }
	\label{fig:Alg2Ds}
\end{figure}
 \begin{figure}
	\centering
	\includegraphics[scale=0.5]{results/samplesofHS-DB.jpg.eps}
	\caption[Hs-DB shapes drawn by single user]{Hs-DB shapes drawn by single user \cite{HeloiseBeautification} }
	\label{fig:samplesofHS-DB.jpg}
\end{figure}
  Figure \ref{fig:correct2.jpg} shows examples of correctly recognized symbol using our system. The figure shows that system recognized some hard to recognize example in both EL-DB and DL-DB. An example of symbols that was not correctly recognized are in Figure \ref{fig:erros}. Most of the wrong classifications were due to how messy the user draw symbols and how similarly they are conceptual. Table \ref{tab:ConfusionMatrix} (confusion matrix) shows the types of error in Hs-DB which shows that the system was confused between parallelogram and trapezoid, moon and arch. Those errors were due to users drawing styles as some user may draw a parallelogram as a trapezoid.

>>>>

%We performed several experiments to evaluate the presented recognition system. Firstly we tested recognition accuracy of shapes in the data set with both algorithms (\textsl{AlgS1} and \textsl{AlgS2}). We also implemented the segmentation algorithm described in \cite{earlyprocess} (\textsl{Alg3} in section \ref{sec:BenchMarckAlgorithm} )  to use as reference to compare it with our swarm algorithms. Figure \ref{fig:test1},\ref{fig:testEL} and \ref{fig:testLD}  shows the accuracy achieved by each algorithm. The two swarm algorithms were tested with and without the ellipse fitting module. The ellipse fitting module appears to be superior. The result shows that combining both algorithms (\textsl{AlgS1} and \textsl{AlgS2}) outperform any single algorithm. %show that combining algorithms achieve higher accuracy than any single algoirthm. 
%improves the results.% with both the \textit{DPSO} algorithms.% The results show that both \textit{DPSO} algorithms achieve better result than other algorithms. 
\begin{figure}
	\centering		
	 \includegraphics[scale=0.4]{paperImages/testAlg.jpg.eps}
	 	\caption{Algorithm Comparison on HS-DB} The recognition rate of different algorithms. 
	 	\label{fig:test1}
	%\caption{Experiments results :} a)    b) c) 
\end{figure} 
\begin{figure}
	\centering		
	 \includegraphics[scale=0.8]{results/AlgLD.eps}
	 	\caption{Algorithm Comparison on LD-DB} The recognition rate of different algorithms. 
	 	\label{fig:testLD}
	%\caption{Experiments results :} a)    b) c) 
\end{figure}

\begin{figure}
	\centering		
	 \includegraphics[scale=0.8]{results/AlgEL.eps}
	 	\caption{Algorithm Comparison on EL-DB} The recognition rate of different algorithms. 
	 	\label{fig:testEL}
	%\caption{Experiments results :} a)    b) c) 
\end{figure}

@@

 The effects of symbol complexity in a dataset were testing in the following experiment. These experiments test how many samples will be required to finally obtain good performance from the recognizer system. In the following experiments, we tested the system using different number of sample per category. 
 Figure \ref{fig:Alg1Ds} and \ref{fig:Alg2Ds} shows that Hs-DB requires more number of sample for training to achieve same result as in other data sets. This is due that it contains less signal and conceptual variation that the other two datasets. Figure \ref{fig:samplesofHS-DB.jpg} shows sample of data collected from one user in Hs-Db it is clear that it has reasonable amount of variation between users but it is limited. Recognizing symbols that contains high variation in drawing style using fewer symbols in training prove the efficiency of our system.
 \begin{figure}
	\centering
		\includegraphics{results/Alg1Ds.eps}
	\caption{AlgS1 on Different Datasets}
	\label{fig:Alg1Ds}
\end{figure}
\begin{figure}
	\centering
		\includegraphics{results/Alg2Ds.eps}
	\caption{AlgS2 on Different Datasets }
	\label{fig:Alg2Ds}
\end{figure}
 \begin{figure}
	\centering
	\includegraphics[scale=0.5]{results/samplesofHS-DB.jpg.eps}
	\caption[Hs-DB Shapes Drawn by Single User]{Hs-DB shapes drawn by single user \cite{HeloiseBeautification} }
	\label{fig:samplesofHS-DB.jpg}
\end{figure}
  Figure \ref{fig:correct2.jpg} shows examples of correctly recognized symbol using our system. The figure shows that system recognized some hard to recognize example in both EL-DB and DL-DB. An example of symbols that was not correctly recognized are in Figure \ref{fig:erros}. Most of the wrong classifications were due to how messy the user draw symbols and how similarly they are conceptual. Table \ref{tab:ConfusionMatrix} (confusion matrix) shows the types of error in Hs-DB which shows that the system was confused between parallelogram and trapezoid, moon and arch. Those errors were due to users drawing styles as some user may draw a parallelogram as a trapezoid.
